Interacting Classical Gas

### 2016-09-22 Interacting Classical Gas_Zhiyu.tex
Sept 22

\documentclass[a4paper,onecolumn,12pt]{article}
\usepackage{amsmath}
 \usepackage{amsfonts}
 \usepackage{amssymb}
 \usepackage{graphicx}
 \usepackage{subfigure}
 \usepackage{enumerate}
 \usepackage{verbatim}% for \begin{comment} \end{comment}
 \begin{document}
 \title{Interacting Classical Gas}
 \author{Zhiyu}
 \maketitle
 \tableofcontents
 \newpage

@@

@@

%-------------%
\begin{comment}
\subparagraph{Detailed discussion on two-particle motion}
From now on, let's stand in the the frame of center of mass to observe the motion of two-particle system. In this frame, without interaction, we will find two particles sitting symmetrically in an equivalent harmonic trap (black curve), whose shape is identical to the trap we see in the static frame. As a result, there frequency of relative motion is exactly $2\omega$(since two particle are identical). We label the position of center of mass as 0. And we may only analyse the motion on positive axis since positive and negative are symmetric.

\begin{figure}
\subfigure[]{
\begin{minipage}[b]{0.3\textwidth}
\includegraphics[scale=0.17]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_1.png} 
\end{minipage}
}
\subfigure[]{
\begin{minipage}[b]{0.3\textwidth}
\includegraphics[scale=0.17]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_2.png} 
\end{minipage}
}
\subfigure[]{
\begin{minipage}[b]{0.3\textwidth}
\includegraphics[scale=0.17]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_3.png} 
\end{minipage}
}
\centering
\caption{Frequency of relative motion with internal energy in three regime} Numbers in the legend is the value of $\frac{F_0}{m\omega_0^2\sigma}$
\label{fig:thermalization3}
\end{figure}}
\end{comment}
%-------------%

\paragraph{More particles}
Now let's consider the three-particle case. For two particle, the motion is non-chaotic. On the other hand, intuitively, we will say that three-body motion is chaotic so that the system could be ``thermalized" soon. However, in some cases, the time scale of thermalizing could still be very long. Suppose two of them, say, A and B, has small internal energy, which means their distance and relative velocity are both small. Meanwhile, suppose particle C has some energy quite different from A \& B. In this case, A \& B will often be in the interaction, while C will pass both of them at a high speed in each period. How will energy transfer between C and the two-particle system A and B? Since the relative velocity of C and the two-particle system is usually large, C will pass A-B pair in a short time $\tau$ ($\tau\ll\frac{2\pi}{\omega}$). When C pass A, it gives A a push, and then push A back.  As has been discussed in the two-particle case, this process is equivalent to giving A a very small speed($\sim O(\tau)$) in the background of a trap. Since the position and velocity of A and B are both close, the effect of C on A \& B are almost the same (difference$\sim O(\tau\sigma)\sim O(\tau^2)$). In this manner, the passing of particle C only kicks the center of mass of the A-B pair slightly, leaving the internal motion of the pair unaffected. In another word, the existence of C will not have significant effect on the energy transfer between A and B, but only ``dance" with their center of mass. The physics of the ``dance" is similar to the dance between two particle. %We only need to substitute $m$, $F_0$ \& $\sigma$ with their effective counterparts, e.g. change $m$ to $\mu$ , which is the reduced mass of m \& 2m.

@@

The argument above still holds in many-particle case. Once we start from some configuration where n particles have a set of close energy levels $\left\lbrace E_n\right\rbrace $ and another m particles have another set of energy levels close to each other $\left\lbrace E_m\right\rbrace $, and $\left\lbrace E_n\right\rbrace $ is quite different from $\left\lbrace E_n\right\rbrace $, we will find these two systems dancing together on the energy level diagram. 
The discussion above gives us some pictures about the non-ergodic state. For these state, life time is rather long so that once the system reach such configuration (or certain energy distribution), it will take a long time(more than $10^4$ periods for N=5 case) to decay.

\subsection{Thermalization condition}
The main obstruct to get an thermalized state (which can be examined by observing distribution) is the low frequency oscillation mentioned before. Because once these modes are excited, the relaxing time could be very long($\textgreater 10^4$). As a result, to achieve ergodic state, we have to avoid such low frequency oscillation. According to our discussion before, the solution is to make internal energy of each two-particle pair not ``too large". Though it is impossible to express the internal energy of every pair in terms of the total energy $E$, we can estimate it by the energy interval, which is $\frac{E}{N}$. At least they are of the same order. The thermalization condition could be given by:
$F_0\sigma\sim\frac{E}{N}$

@@

As is shown in fig.\ref{fig:thermalization5} above, the critical point for reaching Boltzmann distribution is $F_0=5$ while the energy interval of particles $\sim 10$, as we expected, they are of the same order. As a supplementary proof of our argument, fig.\ref{fig:thermalization6} and fig.\ref{fig:thermalization7} show the great difference of single-particle energy between $F_0=2$ $\&$ $F_0=10$ at $E=100$, i.e. in the former one there is always some particle maintained at high excitation, while in the latter the system probably goes to ergodic. Till now, we have verified that the criteria of non-ergodic and ergodic state, which is $\frac{NF_0\sigma}{E}\sim1 $ , and corresponding feature of their energy distribution.

\newpage
\subsection{Verifying Boltzmann distribution}
Thermalization could have different definition. In our system, the "thermalization" we want to find means "losing all the memory of initial state". One of the most important information of initial state is energy distribution. We can check whether a system has gone to equilibrium by measuring its energy distribution.

\paragraph{energy distribution}
For an isothermal system, the energy distribution of the whole system follows the Boltzmann distribution in equilibrium state. However, for an isolated system where the total energy is conserved, it not obvious to draw some strict conclusion about the distribution.

Intuitively, one will expect that if we measure the energy of a subsystem , e.g. one particle, then we will get a Boltzmann distribution because the rest part of the system serves as a bath for this particle. The temperature of this isolated system is defined according to $Nk_BT=E$. It is evident that this argument only hold when the energy of the single particle is not too big--if one particle has 50\% of the total energy, the rest could no longer be think of as a good bath.

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=5_F0=10000.eps}
\caption{Energy distribution, N=5, F0=10000}
\label{fig:thermalization8}
\includegraphics[scale=0.47]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=10_E=1000_edit.eps}
\caption{Energy distribution, N=10, E=1000}
\label{fig:thermalization9}
\includegraphics[scale=0.52]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution2_at_N=20_F0=10000.eps} 
\caption{Energy distribution, N=20, F0=10000}
\label{fig:thermalization10}
\end{figure}

\begin{flushleft}
To take the first one as an example, Y axis is logarithmically scaled. X axis is the ratio between single particle energy (where half of interaction is taken into account) and total energy of the system. The blue dotted line is the predicted Boltzmann distribution (normalized according to counts). Notice that normalizing of the Boltzmann line only change the intercept, leaving slope untouched, which means the slope is the only thing to compare. In  Energy ratio smaller than 30\%, the experiment (colourful curves) fits well with the prediction. When energy of a single particle is higher, one can think of the "bath" formed by the remaining part has lower temperature, thus counts decrease faster to zero than Boltzmann law.

@@

\newpage
\section{Relaxation in Phase-space (unfinished)}
Till now we have verified the energy distribution will go to Boltzmann distribution. However, even if a system have reached Boltzmann distribution, it doesn't mean that the system has completely ``forgotten" its initial state. There is other information that could still exist, for instance, the shape of distribution cloud in phase-space. One of the reasons why we care about this quantity is that it has a strong effect on breathing behaviour. For instance, if the distribution cloud is a thin ellipse (all particles oscillate in phase), the amplitude of oscillation of the cloud radius will be very large. On the contrary, if the cloud is a circle (particles phase of oscillation are completely random), we will not see oscillation at all. Going to equilibrium not only require the thermalization mentioned in last section, but also require reaching a stable configuration in phase-space distribution (relaxation).

@@

From fig.\ref{fig:relaxationPS1}, no evidence shows the shape of cloud will converge. Maybe the fluctuation of S is so large that make it hard to identify the convergence of S. The only way to solve this problem is using more particle simulation to suppress the fluctuation, while the cost is that the simulation time will be limited.

\begin{figure}
\centering
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000.eps} 
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000_average.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000_sup.eps}
\caption{N=20, F0=1000, E=3000, initial S=1}
Different from N=5 case, this time the fluctuation of S is not that large. In return, with an average over every 30s, the S only fluctuate between 0.5 and 0.2
\label{fig:relaxationPS2}
\end{figure}
\begin{figure}
\centering
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000.eps} 
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_average.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_sup.eps}
\caption{N=20, F0=1000, E=10000, initial S=1}
\label{fig:relaxationPS3}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0.eps} 
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_average.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_sup.eps}
\caption{N=20, F0=1000, E=10000, Initial S=0.05}
\label{fig:thermailzationPS4}
\end{figure}

@@

\subsection{Correspondence between energy distribution, behaviour of shape-factor and oscillation of R(t)}
\begin{figure}[hbtp]
\begin{center}
\subfigure[$E=3E5$]{
\begin{minipage}[n]{0.4\textwidth}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=3E5.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_single-particle-Energy_relaxed_N=20_F0=1E4_E=3E5.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=3E5.eps}   
\end{minipage}
}
\subfigure[$E=2E5$]{
\begin{minipage}[n]{0.4\textwidth}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=2E5.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_single-particle-Energy_relaxed_N=20_F0=1E4_E=2E5.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=2E5.eps}   
\end{minipage}
}
\subfigure[$E=1E5$]{
\begin{minipage}[n]{0.4\textwidth}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=1E5.eps}

@@

\subsection{Lyapunov Exponents(unfinished)}
Lyapunov exponents describes how fast one orbit diverge from its nearby orbits in phase-space. The largest LE reflects  the time scale that system lose its memory in phase-space. We will measure the largest LE along our trajectory and plot its distribution.

Before discussion about the mechanism of $\delta$, let us first introduce a approach to simplify this problem:

\subsection{Estimating Breathing Frequency}
What mechanism leads to the precession motion? To answer this question we may turn to two-particle case first. When interaction is very strong, the effect of interaction is equivalent to exchanging momentum when two particles approach each other at distance $\sigma$. In the rotating frame in phase-space, this process can be interpret as follows:

@@

When F0 is not that large, the frequency behaviour seems complicated (see fig.\ref{Breathingfrequency1}). Usually, when F0 increase, frequency goes down below 2 first and then rise up and converge to some value higher than 2. The reason could also be well understood with the mechanism described before. In the former discussion, we goes to high F0 limit, which means particles exchange momentum in infinitesimal time. For F0 is not very big, the finite interaction time should be taken into consideration. During this time, the behaviour of each particle in phase space is exactly moving along the direction of the real P axis at 'velocity' $F0/m$. Since the real P axis is rotating counter-clockwise, the particle will follow the circular trajectory(orange and green dashed line in fig.\ref{Breathingfrequency3}) the $\alpha$ that we once use to estimate the precession motion should decrease with the increase of interaction time. There should be some ``critical point" where $\alpha$ goes from plus to minus (dashed green line). At this point, we will see the precession stop so that the frequency is 2. Thus the relation between frequency and F0 shown in fig.\ref{Breathingfrequency1} is well explained.

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_differentF0_scanF0_1.eps}
\caption{frequency for N=20}
\end{figure}

\section{Supplement}
The picture of breathing frequency is simple in real space. When two particle bounce, they exchange momentum immediately. It can be interpret as particle A carries its momentum $P_A$ and jump $\sigma$ to the right, while particle B carries its momentum $P_B$ and jump $\sigma$ to the left. In this manner, every collision will save a particle some time $\frac{\sigma}{v}$ . Since $v$ is proportional to R while the number of collision each particle experiences in one period of harmonic oscillation can be estimated by N, we will retrieve $\delta\sim N^{\frac{3}{2}}E^{-\frac{1}{2}}$.

>>>>

\documentclass[a4paper,onecolumn,12pt]{article}
\usepackage{amsmath}
 \usepackage{amsfonts}
 \usepackage{amssymb}
 \usepackage{graphicx}
 \usepackage{subfigure}
 \usepackage{enumerate}
 \usepackage{verbatim}% for \begin{comment} \end{comment}
 \usepackage{color}
 \begin{document}
 \title{Interacting Classical Gas}
 \author{Zhiyu}
 \maketitle
 \tableofcontents
 \newpage

@@

\subsection{overview of the system}
\paragraph{relation between Radius and Energy}
radius R is defined as the mean-square-root of each particles position $\left\lbrace x_i\right\rbrace$. When E is very large, the interaction energy can be omitted, so E is dominated by the kinetic energy and potential energy of harmonic oscillators. Thus, $E=2*\frac{1}{2}\omega_0^2*\sum_{i}x_i^2=N\omega_0^2R^2$ 
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{D:/OriginUserfiles/MPI_internship/E_R_fitting.jpg}
-\caption{E-R} This picture shows $E=kR^2$ when energy is large. ($k=N\omega_0^2$)
\end{figure}

\paragraph{Ground states}
For the ground state of this system, one could predict that \\(1) When the sigma is larger than the size of the cloud (in view of the scaling behaviour, large $\sigma$ is equivalent to \textbf{small F0 limit} when we fix $\sigma=1$), it can be easily shown that the ground state is crystal-like, since all every particle keep a equal distance with its nearest neighbours, which is $\frac{2F0}{\omega_0^2}$. The low-lying excitation is particles' independent harmonic oscillation around their equilibrium position.\\(2) When \textbf{F0 is very large} the molecules act like a hardcore gas, while the size of particle is just $\sigma$.

In the picture below, you can see this crossover from the ``solid-like" limit to the ``hardcore gas" limit.

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/groundstate1.eps}
\caption{particles' position at ground states }
\end{figure}

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/Eg1.eps}
\caption{ground state Energy with $F_0$}
\end{figure}

The mechanism that deviate breathing frequency from 2 is simple in real space. When two particle bounce, they exchange momentum immediately. It can be interpret as particle A carries its momentum $P_A$ and jump $\sigma$ to the right, while particle B carries its momentum $P_B$ and jump $\sigma$ to the left. In this manner, every collision will save a particle some time $\frac{\sigma}{v}$ . Since $v$ is proportional to R while the number of collision each particle experiences in one period of harmonic oscillation can be estimated by N, we will get $\delta\sim N^{\frac{3}{2}}E^{-\frac{1}{2}}$.

To see this picture better, let us first introduce a approach to simplify this problem:

{\color{red}{ONE SET OF PICTURES HERE TO SHOW THE TIME EVOLUTION OF THE CLOUD IN PHASE-SPACE:}}
N=20, same E and F0, several initial states:
Stationary frame: T/4 T/2 3T/4 T
rotating frame: T/4 T/2 3T/4 T

\subsection{Estimating Breathing Frequency}
Let us begin with two-particle case. When interaction is very strong, the effect of interaction is equivalent to exchanging momentum when two particles approach each other at distance $\sigma$. In the rotating frame in phase-space, this process can be interpret as follows:

When F0 is not that large, the frequency behaviour seems complicated (see fig.\ref{Breathingfrequency1}). Usually, when F0 increase, frequency goes down below 2 first and then rise up and converge to some value higher than 2. The reason could also be well understood with the mechanism described before. In the former discussion, we goes to high F0 limit, which means particles exchange momentum in infinitesimal time. For F0 is not very big, the finite interaction time should be taken into consideration. During this time, the behaviour of each particle in phase space is exactly moving along the direction of the real P axis at 'velocity' $F0/m$. Since the real P axis is rotating counter-clockwise, the particle will follow the circular trajectory(orange and green dashed line in fig.\ref{Breathingfrequency3}) the $\alpha$ that we once use to estimate the precession motion should decrease with the increase of interaction time. There should be some ``critical point" where $\alpha$ goes from plus to minus (dashed green line). At this point, we will see the precession stop so that the frequency is 2.

@@

\paragraph{More particles}
Now let's consider the three-particle case. For two particle, the motion is non-chaotic. On the other hand, intuitively, we will say that three-body motion is chaotic so that the system could be ``thermalized" soon. However, in some cases, the time scale of thermalizing could still be very long. Suppose two of them, say, A and B, has small internal energy, which means their distance and relative velocity are both small. Meanwhile, suppose particle C has some energy quite different from A \& B. In this case, A \& B will often be in the interaction, while C will pass both of them at a high speed in each period. How will energy transfer between C and the two-particle system A and B? Since the relative velocity of C and the two-particle system is usually large, C will pass A-B pair in a short time $\tau\sim\frac{\sigma}{R}$ ($\tau\ll\frac{2\pi}{\omega}$). C gives A a push when approaching it, and then push A back when leaving.  As has been discussed in the two-particle case, this process is equivalent to giving A a very small speed($\sim O(\frac{\sigma}{R})$) in the background of a trap. Since both the position and velocity of A and B are close($|x_A-x_B|\sim\sigma$), the velocity increase of A \& B are almost the same (difference$\sim O(\frac{\sigma^2}{R^2})$). In this manner, the passing of particle C only kicks the center of mass of the A-B pair slightly, leaving the internal motion of the pair unaffected. In another word, the existence of C will not have significant effect on the energy transfer between A and B, but only ``dance" with their center of mass. The physics of the ``dance" is similar to the dance between two particle. As is shown in fig.\ref{fig:thermalization4}, the particles with energy close to each other tends to form a pair with small internal energy and the pair's internal energy transfer is relatively stable. %We only need to substitute $m$, $F_0$ \& $\sigma$ with their effective counterparts, e.g. change $m$ to $\mu$ , which is the reduced mass of m \& 2m.

@@

The argument above still holds in many-particle case. Once we start from some configuration where n particles have a set of close energy levels $\left\lbrace E_n\right\rbrace $ and another m particles have another set of energy levels close to each other $\left\lbrace E_m\right\rbrace $, and $\left\lbrace E_n\right\rbrace $ is quite different from $\left\lbrace E_n\right\rbrace $, we will find these two systems oscillating on the energy level diagram at low frequency. 
The discussion above gives us some pictures about the non-ergodic state. For these state, life time is rather long so that once the system reach such configuration (or certain energy distribution), it will take a long time(more than $10^4$ periods for N=5 case) to decay.

\subsection{Thermalization condition}
The main obstruct to get an thermalized state (which can be examined by observing distribution) is the low frequency oscillation mentioned before. Because once these modes are excited, the relaxing time could be very long($\textgreater 10^4$). As a result, to achieve ergodic state, we have to avoid such low frequency oscillation. According to our discussion before, the solution is to make internal energy of each two-particle pair not ``too large". Though it is impossible to express the internal energy of every pair in terms of the total energy $E$, we can estimate it by the average energy, which is $\frac{E}{N}$. At least they are of the same order. The thermalization condition could be given by:
$F_0\sigma\sim\frac{E}{N}$

@@

As is shown in fig.\ref{fig:thermalization5} above, the critical point for reaching Boltzmann distribution is $F_0=5$ (we always set $\sigma=1$), while the average energy $\sim 10$, as we expected, they are of the same order. As a supplementary proof of our argument, fig.\ref{fig:thermalization6} and fig.\ref{fig:thermalization7} show the great difference of single-particle energy between $F_0=2$ $\&$ $F_0=10$ at $E=100$, i.e. in the former one there is always some particle maintained at high excitation, while in the latter the system probably goes to ergodic. To date, we have verified that the threshold of thermalization, which is $\frac{NF_0\sigma}{E}\sim1 $ , and corresponding feature of their energy distribution in two side of the threshold.

\newpage
\subsection{Verifying Boltzmann distribution}
Thermalization could have different definition. In our system, the ``thermalization" we want to find means ``losing all the memory of initial state". One of the most important information of initial state is energy distribution. We can check whether a system has gone to equilibrium by measuring its energy distribution.

\paragraph{energy distribution}
For an isothermal system, the energy distribution of the whole system follows the Boltzmann distribution in equilibrium state. However, to our knowledge, there is not any obvious conclusion about the distribution for an isolated system where the total energy is conserved.

But intuitively, one will expect that if we measure the energy of a subsystem , e.g. one particle, then we will get a Boltzmann distribution because the rest part of the system serves as a bath for this particle. The temperature of this isolated system is defined according to $Nk_BT=E$. It is evident that this argument only hold when the energy of the single particle is not too big --- if one particle take up 50\% of the total energy, the rest could no longer be thought of as a good bath.

@@

\newpage
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=5_F0=10000.eps}
\caption{Energy distribution, N=5, F0=10000}
\label{fig:thermalization8}

\includegraphics[scale=0.47]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=10_E=1000_edit.eps}
\caption{Energy distribution, N=10, E=1000}
\label{fig:thermalization9}

\includegraphics[scale=0.52]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution2_at_N=20_F0=10000.eps} 
\caption{Energy distribution, N=20, F0=10000}
\label{fig:thermalization10}
\end{figure}

\newpage
\begin{flushleft}
To take the first one as an example, Y axis is logarithmically scaled. X axis is the ratio between single particle energy (where half of interaction is taken into account) and total energy of the system. The blue dotted line is the predicted Boltzmann distribution (normalized according to counts). Notice that normalizing of the Boltzmann line only change the intercept, leaving slope untouched, which means the slope is the only thing to compare. In  Energy ratio smaller than 30\%, the experiment (colourful curves) fits well with the prediction. When energy of a single particle is higher, one can think of the "bath" formed by the remaining part has lower temperature, thus counts decrease faster to zero than Boltzmann law.

@@

\newpage
\section{Relaxation in Phase-space}
To date, we have verified that the energy distribution will go to Boltzmann distribution. However, even if a system have reached Boltzmann distribution, it doesn't mean that the system has completely ``forgotten" its initial state. There is other information that could still exist, for instance, the shape of distribution cloud in phase-space. One of the reasons why we care about this quantity is that it has a strong effect on breathing behaviour. For instance, if the distribution cloud is a thin ellipse (all particles oscillate in phase), the amplitude of oscillation of the cloud radius will be very large. On the contrary, if the cloud is a circle (particles phase of oscillation are completely random), we will not see oscillation at all. Going to equilibrium not only require the thermalization mentioned in last section, but also require reaching a stable configuration in phase-space distribution (relaxation).

@@

From fig.\ref{fig:relaxationPS1}, no evidence shows the shape of cloud will converge. Maybe the fluctuation of S is so large that make it hard to identify the convergence of S. The only way to solve this problem is using more particle simulation to suppress the fluctuation.

\begin{figure}
\centering
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000.eps} 
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000_average.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000_sup.eps}
\caption{N=20, F0=1000, E=3000, initial S=1}
\begin{flushleft}
Different from N=5 case, this time the fluctuation of S is not that large. In return, with an average over every 30s, the S only fluctuate between 0.5 and 0.2
\end{flushleft}
\label{fig:relaxationPS2}
\end{figure}
\begin{figure}
\centering
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000.eps} 
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_average.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_sup.eps}
\caption{N=20, F0=1000, E=10000, initial S=1}
\label{fig:relaxationPS3}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0.eps} 
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_average.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_sup.eps}
\caption{N=20, F0=1000, E=10000, Initial S=0.05}
\label{fig:relaxationPS4}
\end{figure}

@@

\newpage
\subsection{Correspondence between energy distribution, behaviour of shape-factor and oscillation of R(t)}
\begin{figure}[hbtp]
\begin{center}
\subfigure[$E=3E5$]{
\begin{minipage}[n]{0.4\textwidth}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=3E5.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_single-particle-Energy_relaxed_N=20_F0=1E4_E=3E5.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=3E5.eps}   
\end{minipage}
}
\subfigure[$E=2E5$]{
\begin{minipage}[n]{0.4\textwidth}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=2E5.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_single-particle-Energy_relaxed_N=20_F0=1E4_E=2E5.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=2E5.eps}   
\end{minipage}
}
\subfigure[$E=1E5$]{
\begin{minipage}[n]{0.4\textwidth}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=1E5.eps}

@@

\newpage
\subsection{Lyapunov Exponents(unfinished)}
Lyapunov exponents(LE) describes how fast one orbit diverge from its nearby orbits in phase-space. The largest Lyapunov exponents (LLE) reflects  the time scale that system lose its memory in phase-space. We will measure the LLEs along our trajectory and plot its distribution.

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_LLEevolution_F0=1000_E=3000_2.eps}
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_Energy_F0=1000_E=3000_2.eps} 
\caption{N=5, F0=1000, E=3000, Gaussian interaction}
\label{fig:LLEexample1}
\end{figure}
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_LLEevolution_F0=1000_E=10000_1.eps}
\caption{N=5, F0=1000, E=10000, Gaussian interaction}
\label{fig:LLEexample2}
\end{figure}
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_LLEevolution_F0=1000_E=100000_1.eps}
\caption{N=5, F0=1000, E=100000, Gaussian interaction}
\label{fig:LLEexample3}
\end{figure}

Fig.\ref{fig:LLEexample1}, fig.\ref{fig:LLEexample2} and fig.\ref{fig:LLEexample3} serve as examples showing the way I measure LLE: I integrate and average the LLE along the trajectory, usually over 100-1000 time unit, the LLE converge to certain stable value, and then I start another LLE measurement. \textbf{From the examples above, one may judge how good the convergence is and how big the error of LLE measurement can be.}

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.8]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_scanE_9_22.eps}
\caption{LLE distribution for N=5, F0=1000, scan E. (It seems that MATLAB has difficulty changing .fig into .eps files. To get rid of the annoying white lines you may open this figure in MATLAB with .fig format.)}
\label{fig:LLEdistribution1}
\end{figure}

fig.\ref{fig:LLEdistribution1} shows the distribution of LLE by color. The LLE decrease with the growth of Energy. The crucial part is near E=5000. The most probable value of LLE goes down from 1 to 0.1,which indicate that \textbf{the shortest time scale becomes longer than an oscillation period when E is larger than 5000}. And E=5000 is exactly our prediction value of thermalization threshold. So there is a correspondence between energy thermalization and LLE. 
The size of bin(resolution of LLE) in fig.\ref{fig:LLEdistribution1} is 0.01, so when E goes far beyond the thermalization threshold, the LLE distribution is not that clear. We only know that LLE is concentrated close to zero in high E regime.

\section{others(those I haven't organized it into the text in logical order but may be useful)}

\subsection{Evolution of $R(t)$ and $\sqrt{\delta^2R(t)}/R(t)$} 
Results are shown in fig.\ref{fig:others1}

@@

\centering
\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/fluc_of_R_with_time2.eps}
\caption{fluctuation of R with time }
sigma=0.01(short range), $F_0=0.1(black), 1(blue), 10(green) ,100(red)$
\label{fig:others1}
\end{figure}

\subsection{Detailed discussion of two-particle motion}
{\color{red}{This chapter previously follow the subsection ``two-particle case" in subsection ``Dynamics study" in section ``Thermalization". But then I found we haven't used these result. So I put it at the end for the time being}}.

From now on, let's stand in the the frame of center of mass to observe the motion of two-particle system. In this frame, without interaction, we will find two particles sitting symmetrically in an equivalent harmonic trap (black curve), whose shape is identical to the trap we see in the static frame. As a result, there frequency of relative motion is exactly $2\omega$(since two particle are identical). We label the position of center of mass as 0. And we may only analyse the motion on positive axis since positive and negative are symmetric.

\begin{figure}
\subfigure[]{
\begin{minipage}[b]{0.3\textwidth}
\includegraphics[scale=0.17]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_1.png} 
\end{minipage}
}
\subfigure[]{
\begin{minipage}[b]{0.3\textwidth}
\includegraphics[scale=0.17]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_2.png} 
\end{minipage}
}
\subfigure[]{
\begin{minipage}[b]{0.3\textwidth}
\includegraphics[scale=0.17]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_3.png} 
\end{minipage}
}
\centering
\caption{Frequency of relative motion with internal energy in three regime} Numbers in the legend is the value of $\frac{F_0}{m\omega_0^2\sigma}$
\label{fig:thermalization3}
\end{figure}
